Choose a License

### 2024-11-27 choose_license.qmd
Remove references to Science Commons
Their argument is likely not upheld anymore as they
advertise other licenses than CC0 for data.

Note, that for data there is, at least in principle, the possibility that a different license applies to the individual entries than to the collective database. For example, if you were to create a database of artworks by others, those artworks would be licensed individually as chosen by the artists, but the license for the database as a whole could be chosen by you. The latter includes the selection of entries, field names and any _sui generis_ database rights. However, if the content was created by you, we recommend you to choose the same license for both content and database. Factual data (like measurements or metadata) should be licensed under [CC0\ 1.0](https://creativecommons.org/publicdomain/zero/1.0/) [@Dryad2011; @ScienceCommons2018] -- otherwise, see @nte-other-work-types for some caveats.

>>>>

Note, that for data there is, at least in principle, the possibility that a different license applies to the individual entries than to the collective database. For example, if you were to create a database of artworks by others, those artworks would be licensed individually as chosen by the artists, but the license for the database as a whole could be chosen by you. The latter includes the selection of entries, field names and any _sui generis_ database rights. However, if the content was created by you, we recommend you to choose the same license for both content and database. Factual data (like measurements or metadata) should be licensed under [CC0\ 1.0](https://creativecommons.org/publicdomain/zero/1.0/) -- otherwise, consult @nte-other-work-types for some caveats.
